Molecular Analysis

### 2023-10-19 analysis/aud_analysis.Rmd
change color in plots and reorder

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  mutate(coughs_per_min = n_coughs / TT) %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = coughs_per_min)) +
  geom_boxplot2(width.errorbar = .3, width = .4) +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 93%", y_position = 6.25, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5) +
  scale_fill_manual(values = wes_palette("Royal1")) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(add = c(0, .66))) +
  labs(title = "d", y = "Number of coughs per min", x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

>>>>

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  mutate(coughs_per_min = n_coughs / TT) %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = coughs_per_min)) +
  geom_boxplot2(width.errorbar = .3, width = .4) +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 93%", y_position = 6.25, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5) +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(add = c(0, .66))) +
  labs(title = "d", y = "Number of coughs per min", x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

### 2023-10-19 analysis/env_analysis.Rmd
change color in plots and reorder

```{r}
# only particle number concentration
boxpl_cn <- env_epi_data %>%
  dplyr::select(class, date, aircleaner, Cn) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = Cn)) +
  geom_boxplot2(width.errorbar = .3, width = .4) +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 100%", y_position = 240, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5) +
  scale_fill_manual(values = wes_palette("Royal1")) +
  scale_y_continuous(expand = expansion(add = c(0, 30)), limits = c(0, NA)) +
  labs(title = "b", y = expression("Aerosol concentration (1/cm"^3*")"), x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

@@

```{r}
# particle concentrations
boxpl_pc <- env_epi_data %>%
  dplyr::select(class, date, weekday, aircleaner, Cn, PM1, PM25, PM4, PM10) %>%
  melt(c("class", "date", "weekday", "aircleaner")) %>%
  rename(`Air Cleaner` = aircleaner,
         Class = class) %>%
  ggplot(aes(x = `Air Cleaner`, color = `Air Cleaner`, y = value)) +
  facet_wrap(~ variable, scales = "free_y", nrow = 1, dir = "h", labeller = as_labeller(vars_labels, label_parsed)) +
  geom_boxplot2() +
  geom_jitter(aes(shape = Class), alpha = .3, width = .2) +
  scale_color_manual(values = wes_palette("Royal1")) +
  scale_shape_manual(values = c(2,20)) +
  labs(title = "a") +
  theme_custom() +
  theme(axis.title.y = element_blank(), legend.position = "top",
        plot.title.position = "plot") +
  guides(color = "none")

@@

# other variables
boxpl_oth <- env_epi_data %>%
  dplyr::select(class, date, weekday, aircleaner, CO2, AER, rH, Temp) %>%
  melt(c("class", "date", "weekday", "aircleaner")) %>%
  rename(`Air Cleaner` = aircleaner,
         Class = class) %>%
  ggplot(aes(x = `Air Cleaner`, color = `Air Cleaner`, y = value)) +
  facet_wrap(~ variable, scales = "free_y", nrow = 1, dir = "h", labeller = as_labeller(vars_labels, label_parsed)) +
  geom_boxplot2() +
  geom_jitter(aes(shape = Class), alpha = .3, width = .2) +
  scale_color_manual(values = wes_palette("Royal1")) +
  scale_shape_manual(values = c(2,20)) +
  theme_custom() +
  theme(axis.title.y = element_blank(), legend.position = "top") +
  guides(color = "none")
save_plot(boxpl_oth, pdf_file = "../results/env-data/otherVars-boxplot.pdf", w = 16, h = 8)
```

@@

# create estimation results figure
effects_env_main <- draws_filt %>%
  mutate(outcome = factor(outcome, levels = (c("Cn", "PM1", "PM25", "PM4", "PM10")))) %>%
  group_by(outcome) %>%
  mean_qi(.width = c(0.5, 0.8, 0.95)) %>%
  ungroup() %>%
  arrange(desc(.width)) %>%
  mutate(`.width` = factor(`.width`, levels = rev(c(.5, .8, .95)))) %>%
  ggplot() +
  geom_rect(aes(xmin = .lower, xmax = .upper, ymin = 75, ymax = 125, fill = `.width`)) +
  geom_segment(aes(x = aircleaner, xend = aircleaner, y = 75, yend = 125), size = 1.5 / cm(1)) +
  geom_point(aes(x = aircleaner, y = 100), size = 3, fill = "white", shape = 21) +
  facet_wrap(~ outcome, nrow = 1, labeller = as_labeller(vars_labels_no_units, label_parsed)) +
  scale_fill_manual(values = wes_palette("Royal1")[c(3,4,2)]) +
  scale_y_continuous(expand = expansion(mult = c(0.25, 0.25))) +
  scale_x_continuous(limits = c(50, 100), expand = expansion(mult = c(0.1, 0.1)), breaks = c(50, 75, 100)) +
  labs(x = "Estimated reduction (%)", y = "Type", fill = "CrI", title = "b") +
  theme_custom() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(color = "white"),
        axis.ticks.y = element_blank(),
        legend.position = "top", legend.direction = "horizontal",
        legend.key.height = unit(.25, "cm"), legend.key.width = unit(.35, "cm"), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title.position = "plot",
        panel.spacing = unit(20, units = "pt")) 
save_plot(effects_env_main, 
          pdf_file = "../results/env-data/estimation-results-figure.pdf",
          eps_file = "../results/env-data/estimation-results-figure.eps",
          w = 16, h = 5)
```

>>>>

```{r}
# only particle number concentration
boxpl_cn <- env_epi_data %>%
  dplyr::select(class, date, aircleaner, Cn) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = Cn)) +
  geom_boxplot2(width.errorbar = .3, width = .4) +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 100%", y_position = 240, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5) +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(expand = expansion(add = c(0, 30)), limits = c(0, NA)) +
  labs(title = "c", y = expression("Aerosol concentration (1/cm"^3*")"), x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

@@

```{r}
# particle concentrations
boxpl_pc <- env_epi_data %>%
  dplyr::select(class, date, weekday, aircleaner, Cn, PM1, PM25, PM4, PM10) %>%
  melt(c("class", "date", "weekday", "aircleaner")) %>%
  rename(`Air Cleaner` = aircleaner,
         Class = class) %>%
  ggplot(aes(x = `Air Cleaner`, color = `Air Cleaner`, y = value)) +
  facet_wrap(~ variable, scales = "free_y", nrow = 1, dir = "h", labeller = as_labeller(vars_labels, label_parsed)) +
  geom_boxplot2() +
  geom_jitter(aes(shape = Class), alpha = .3, width = .2) +
  scale_color_manual(values = bluegrey) +
  scale_shape_manual(values = c(2,20)) +
  labs(title = "a") +
  theme_custom() +
  theme(axis.title.y = element_blank(), legend.position = "top",
        plot.title.position = "plot") +
  guides(color = "none")

boxpl_pc

@@

# other variables
boxpl_oth <- env_epi_data %>%
  dplyr::select(class, date, weekday, aircleaner, CO2, AER, rH, Temp) %>%
  melt(c("class", "date", "weekday", "aircleaner")) %>%
  rename(`Air Cleaner` = aircleaner,
         Class = class) %>%
  ggplot(aes(x = `Air Cleaner`, color = `Air Cleaner`, y = value)) +
  facet_wrap(~ variable, scales = "free_y", nrow = 1, dir = "h", labeller = as_labeller(vars_labels, label_parsed)) +
  geom_boxplot2() +
  geom_jitter(aes(shape = Class), alpha = .3, width = .2) +
  scale_color_manual(values = bluegrey) +
  scale_shape_manual(values = c(2,20)) +
  theme_custom() +
  theme(axis.title.y = element_blank(), legend.position = "top") +
  guides(color = "none")

boxpl_oth

save_plot(boxpl_oth, pdf_file = "../results/env-data/otherVars-boxplot.pdf", w = 16, h = 8)
```

@@

# create estimation results figure
effects_env_main <- draws_filt %>%
  mutate(outcome = factor(outcome, levels = (c("Cn", "PM1", "PM25", "PM4", "PM10")))) %>%
  group_by(outcome) %>%
  mean_qi(.width = c(0.5, 0.8, 0.95)) %>%
  ungroup() %>%
  arrange(desc(.width)) %>%
  mutate(`.width` = factor(`.width`, levels = rev(c(.5, .8, .95)))) %>%
  ggplot() +
  geom_rect(aes(xmin = .lower, xmax = .upper, ymin = 75, ymax = 125, fill = `.width`)) +
  geom_segment(aes(x = aircleaner, xend = aircleaner, y = 75, yend = 125), size = 1.5 / cm(1)) +
  geom_point(aes(x = aircleaner, y = 100), size = 3, fill = "white", shape = 21) +
  facet_wrap(~ outcome, nrow = 1, labeller = as_labeller(vars_labels_no_units, label_parsed)) +
  scale_fill_brewer() +
  scale_y_continuous(expand = expansion(mult = c(0.25, 0.25))) +
  scale_x_continuous(limits = c(50, 100), expand = expansion(mult = c(0.1, 0.1)), breaks = c(50, 75, 100)) +
  labs(x = "Estimated reduction (%)", y = "Type", fill = "CrI", title = "b") +
  theme_custom() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(color = "white"),
        axis.ticks.y = element_blank(),
        legend.position = "top", legend.direction = "horizontal",
        legend.key.height = unit(.25, "cm"), legend.key.width = unit(.35, "cm"), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title.position = "plot",
        panel.spacing = unit(20, units = "pt"))

effects_env_main

save_plot(effects_env_main, 
          pdf_file = "../results/env-data/estimation-results-figure.pdf",
          eps_file = "../results/env-data/estimation-results-figure.eps",
          w = 16, h = 5)
```

### 2023-10-19 analysis/epi_analysis.Rmd
change color in plots and reorder

# number of cases by week
cases_by_cond_pl <- epi_data %>%
  group_by(aircleaner) %>%
  summarize(cases = sum(new_cases)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, y = cases, fill = aircleaner)) +
  geom_bar(stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = cases), size = 8 / cm(1), vjust = -1) +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 91%", y_position = 27, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5, tip_length = .075) +
  labs(x = "Air cleaner", y = "Number of respiratory cases", fill = "Air cleaner", title = "c") +
  scale_fill_manual(values = wes_palette("Royal1")[1:2]) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")

@@

avoid_infections_pl <- avoid_infections  %>%
  ggplot() +
  geom_rect(aes(xmin = .lower, xmax = .upper, ymin = 7.5, ymax = 12.5, fill = `.width`)) +
  geom_segment(aes(x = infections, xend = infections, y = 7.5, yend = 12.5), size = 1.5 / cm(1)) +
  geom_point(aes(x = infections, y = 10), size = 3, fill = "white", shape = 21) +
  facet_wrap(~ type, ncol = 1) +
  scale_fill_manual(values = wes_palette("Royal1")[c(3,4,2)]) +
  scale_y_continuous(expand = expansion(mult = c(0.25, 0.25))) +
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0)), breaks = seq(0, 200, 25)) +
  labs(x = "Estimated number of infections", y = "Scenario", fill = "CrI") +
  theme_custom() +
  theme(axis.title.y = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.ticks.y = element_blank(),
        legend.position = "top", legend.direction = "horizontal",
        legend.key.height = unit(.25, "cm"), legend.key.width = unit(.35, "cm"), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title.position = "plot",
        panel.spacing = unit(20, units = "pt"),
        strip.text.x = element_text(margin = margin(b = 5)))

@@

fitted_cases_pl <- ggplot(mapping = aes(x = week)) +
  stat_lineribbon(data = fitted_cases,
                  mapping = aes(y = estimated_cases),
                  .width = c(0.5, 0.8, 0.95), color = "brown") +
  geom_line(data = fitted_cases %>% group_by(week) %>% slice(1),
            mapping = aes(y = true_cases, color = "Observed"), size = 1.5) +
  scale_fill_manual(values = wes_palette("Royal1")[c(3,4,2)]) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0, NA), breaks = scales::breaks_width(2)) +
  scale_color_manual(values = "black") +
  labs(y = "Number of new infections", x = "Study week", fill = "Estimated (CrI)") +
  theme_custom() +
  theme(legend.position = "top") +
  guides(color = guide_legend(title = element_blank()))
fitted_cases_pl

>>>>

# number of cases by week
cases_by_cond_pl <- epi_data %>%
  group_by(aircleaner) %>%
  summarize(cases = sum(new_cases)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, y = cases, fill = aircleaner)) +
  geom_bar(stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = cases), size = 8 / cm(1), vjust = -1) +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 91%", y_position = 27, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5, tip_length = .075) +
  labs(x = "Air cleaner", y = "Number of respiratory cases", fill = "Air cleaner", title = "a") +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")

@@

avoid_infections_pl <- avoid_infections  %>%
  ggplot() +
  geom_rect(aes(xmin = .lower, xmax = .upper, ymin = 7.5, ymax = 12.5, fill = `.width`)) +
  geom_segment(aes(x = infections, xend = infections, y = 7.5, yend = 12.5), size = 1.5 / cm(1)) +
  geom_point(aes(x = infections, y = 10), size = 3, fill = "white", shape = 21) +
  facet_wrap(~ type, ncol = 1) +
  scale_fill_brewer() +
  scale_y_continuous(expand = expansion(mult = c(0.25, 0.25))) +
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0)), breaks = seq(0, 200, 25)) +
  labs(x = "Estimated number of infections", y = "Scenario", fill = "CrI") +
  theme_custom() +
  theme(axis.title.y = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.ticks.y = element_blank(),
        legend.position = "top", legend.direction = "horizontal",
        legend.key.height = unit(.25, "cm"), legend.key.width = unit(.35, "cm"), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title.position = "plot",
        panel.spacing = unit(20, units = "pt"),
        strip.text.x = element_text(margin = margin(b = 5)))

avoid_infections_pl

@@

fitted_cases_pl <- ggplot(mapping = aes(x = week)) +
  stat_lineribbon(data = fitted_cases,
                  mapping = aes(y = estimated_cases),
                  .width = c(0.5, 0.8, 0.95), color = "darkblue") +
  geom_line(data = fitted_cases %>% group_by(week) %>% slice(1),
            mapping = aes(y = true_cases, color = "Observed"), size = 1.5) +
  scale_fill_brewer() +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0, NA), breaks = scales::breaks_width(2)) +
  scale_color_manual(values = "black") +
  labs(y = "Number of new infections", x = "Study week", fill = "Estimated (CrI)") +
  theme_custom() +
  theme(legend.position = "top") +
  guides(color = guide_legend(title = element_blank()))

fitted_cases_pl

### 2023-10-19 analysis/mol_analysis.Rmd
change color in plots and reorder

pos_cond_pl <- df_pos_stud %>%
  ggplot(aes(x = aircleaner, y = n_pos)) +
  geom_bar(mapping = aes(fill = aircleaner), stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = n_pos), size = 8 / cm(1), vjust = -1) +
  geom_segment(data = data.frame(x = .5, xend = .5, y = 30, yend = 29), mapping = aes(x = x, xend = xend, y = y, yend = yend), color = "white") +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 65%", y_position = 30, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5, tip_length = .1) +
  labs(x = "Air cleaner", y = "Number of positive saliva samples", title = "a") +
  scale_fill_manual(values = wes_palette("Royal1")[1:2]) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")

>>>>

pos_cond_pl <- df_pos_stud %>%
  ggplot(aes(x = aircleaner, y = n_pos)) +
  geom_bar(mapping = aes(fill = aircleaner), stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = n_pos), size = 8 / cm(1), vjust = -1) +
  geom_segment(data = data.frame(x = .5, xend = .5, y = 30, yend = 29), mapping = aes(x = x, xend = xend, y = y, yend = yend), color = "white") +
  ggsignif::geom_signif(annotations = "PP(Yes<No) = 65%", y_position = 30, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5, tip_length = .1) +
  labs(x = "Air cleaner", y = "Number of positive saliva samples", title = "b") +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")
